---
title: "Scenario analysis"
bibliography: ../references.bib
csl: ../elsvan.csl
---

## What scenario analyses were conducted?

In the assessment report, @lee_treatments_2023-1 **Table 95** provides a very clear overview of the scenarios explored. It details how these differ from the base case, and justification for the scenario. Further description is also offered elsewhere in the report.

As an example, one of the scenarios is:

| Parameter | Base case | Scenario | Justification |
| - | - | - | - |
| Baseline risk | UK RWE | CheckMate 9ER | Testing impact of baseline risk |

In this scenario, the reference surival curves providing baseline risk for the reference treatments are calculated using clinical trial data, rather than using the real-world evidence.

In addition to the scenarios described in Table 95, there was also an exploratory analysis on the impact of prior adjuvant therapy. This is detailed in section **4.3.5.8** of the assessment report. @lee_treatments_2023-1

## How can these scenarios be run?

To run these scenarios, you'll need to alter the model script (for example, altering `Model_Structure.R`).

A table of scenarios is provided in the excel input sheet and imported into `i` as `i$R_table_scenarios`. This outlines the inputs that will need to be changed in order to run the scenario analysis. Each row in this table has:

* **Scenario category** (e.g. "Model structure")
* **Scenario number** (e.g. 1)
* **Scenario label** (e.g. "PartSA 4 lines" - i.e. using a partitioned survival model instead of state transition)
* **Inputs.required** (i.e. number of inputs to be altered) (e.g. 2)
* A set of columns for each input with:
  * **Sheet** (i.e. source of input in excel) (e.g. "Model settings")
  * **Range** (i.e. named range in excel that imports the input) (e.g. "dd_model_struct")
  * **Value** (e.g. "Partitioned survival)
  * In this example, the second input (as detailed in the subsequent columns) was sheet "Model settings", range "R_max_trt_lines" and value 4

::: {.callout-note collapse="true"}

## View `i$R_table_scenarios`

```{r}
#| output: FALSE
library(knitr, quiet = TRUE)
i <- readRDS("../../2_Scripts/standalone scripts/QC/i.rds")
```
```{r}
kable(i$R_table_scenarios)
```

:::